Limited physiological plasticity and reduced relative variance in physiological rates of ectotherm populations under climate change

### 2024-07-01 ms.qmd
Fixing supp figure code chunk name as it shouldn't be double plotting funnel plots.

@fig-S2; @fig-cvrtrait

@@

  # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
  lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat = "m" & !trait_category =="antiox") %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat = "f" & !is.na(c_accl_time))
  lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat = "t" & !is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))

@@

```{r, fig-S2}
#| label: fig-S2
#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across detailed trait categories for A) marine, B) freshwater and C) terrestrial systems. k = total number of effect size estimates while the numbers in brackets indicate the number of species. Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals. The x-axis is truncated for ease of visualisation. See methods section “Moderator Variables” for a full description of the trait categories. "
#| echo: false

@@

#### *Mean-variance relationships to understand patterns in $lnCVR_{Q_{10}}$*
We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats. We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses. We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.

>>>>

@fig-cvrtrait; @fig-cvrtrait

@@

  # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
  lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m" & !trait_category =="antiox") %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f" & !is.na(c_accl_time))
  lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t" & !is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))

@@

```{r, fig-lnrrtrait}
#| label: fig-lnrrtrait
#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across detailed trait categories for A) marine, B) freshwater and C) terrestrial systems. k = total number of effect size estimates while the numbers in brackets indicate the number of species. Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals. The x-axis is truncated for ease of visualisation. See methods section “Moderator Variables” for a full description of the trait categories. "
#| echo: false

@@

#### *Mean-variance relationships to understand patterns in $lnCVR_{Q_{10}}$*

```{r, mc_models}
#| label: mc_models
#| echo: false
#| include: false

We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats. We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses. We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
